---
title: "REPRODUCTIBE Course Project 1"
author: "jlt75"
date: "22 août 2017"
output: html_document
---




# Load Data  and convert date in date type 



```{r , echo=TRUE}
Activity = read.csv("activity.csv")
Activity$date = as.Date(Activity$date, format = "%Y-%m-%d")

```






# Q1 Histogram 
```{r , echo=TRUE}
ActivityDay = as.data.frame(tapply(Activity$steps, Activity$date, sum, na.rm = TRUE))
ActivityDay$date = as.Date(row.names(ActivityDay), format = "%Y-%m-%d") 
colnames(ActivityDay) = c('totalSteps','date')
```

Plot Histogram 
```{r , echo=TRUE}
hist(ActivityDay$totalSteps, breaks = 20,xlab = "Steps per day",main = "Histogram of steps per day (na.rm)")
```
Mean and median  

```{r , echo=TRUE}
mean(ActivityDay$totalSteps, na.rm= TRUE)
median(ActivityDay$totalSteps, na.rm= TRUE)
``` 


#Q2 number of steps taken, on average  across all days

```{r , echo=TRUE}
ActivityInterval = as.data.frame(tapply(Activity$steps, Activity$interval, mean, na.rm = TRUE))
ActivityInterval$interval = row.names(ActivityInterval)
colnames(ActivityInterval) = c('meanSteps','interval')

plot(ActivityInterval$interval, ActivityInterval$meanSteps, type="l", xlab= "interval", ylab= "number of steps taken, averaged across all days", col="black" , lwd=2)
```
# Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r , echo=TRUE}
Activity$interval[which.max(ActivityInterval$meanSteps)]

```
#Q3 Histogram of steps per day (Filled dataset)

test for Nas 

```{r , echo=TRUE}
summary(Activity)
```
Yes ...  

fill with average number of steps of the interval across all the days

```{r , echo=TRUE}

ActivityFilled = Activity
ActivityFilled = merge(ActivityFilled, ActivityInterval, by = "interval", x.all=TRUE)


ActivityFilled$steps= ifelse(is.na(ActivityFilled$steps), ActivityFilled$meanSteps,ActivityFilled$steps)

summary(ActivityFilled)
```
#Process data  

```{r , echo=TRUE}
ActivityFilledDay = as.data.frame(tapply(ActivityFilled$steps, ActivityFilled$date, sum))
ActivityFilledDay$date = as.Date(row.names(ActivityFilledDay), format = "%Y-%m-%d") 
colnames(ActivityFilledDay) = c('totalSteps','date')
``` 

And plot the histogram  
```{r , echo=TRUE}
hist(ActivityFilledDay$totalSteps, breaks = 20,xlab = "Steps per day",main = "Histogram of steps per day (Filled dataset)")
```


Mean and median 
```{r , echo=TRUE}
mean(ActivityFilledDay$totalSteps)
median(ActivityFilledDay$totalSteps)

```
Do these values differ from the estimates from the first part of the assignment? 
What is the impact of imputing missing data on the estimates of the total daily number of steps?

difference of means ad medians 
```{r , echo=TRUE}
mean(ActivityFilledDay$totalSteps)-mean(ActivityDay$totalSteps)
median(ActivityFilledDay$totalSteps)-median(ActivityDay$totalSteps)
```


#Q4 plot weekday and weekend average number pf steps
```{r , echo=TRUE}
ActivityFilled$weekend = ifelse(weekdays(ActivityFilled$date) == "samedi" | weekdays(ActivityFilled$date) == "dimanche", "weekend", "weekday")

ActivityIntervalFilled = aggregate(ActivityFilled$steps,by=list(ActivityFilled$interval,ActivityFilled$weekend),FUN=mean,na.rm=TRUE)
colnames(ActivityIntervalFilled) = c('interval','weekend','meanSteps')
library(ggplot2)
ggplot(aes(x=interval,y=meanSteps),data= ActivityIntervalFilled)+geom_line()+facet_wrap(~ActivityIntervalFilled$weekend)
```
#End 
